---
title: "Machine Learning for Economists: <br>ml4econ"
output: github_document
---

### [Machine Learning for Economists](https://ml4econ.rbind.io/)

---

```{r child = here::here('content/schedule/index.md')}
```

---

## Overview

This course covers topics that range between machine learning (ML) and econometrics. In particular, we will discuss concepts from the world of ML that can potentially contribute to empirical research in economics. The course will cover basic machine learning (supervised and unsupervised) methods, with an emphasis on the challenges and opportunities of integrating these methods in economics, and the relevance of ML to policy analysis and causal inference. The various topics are illustrated through applications, reading empirical articles, and doing applied work.

## Pre-work

```{r child = here::here('content/materials/prework/index.Rmd')}
```

---

[![forthebadge](https://forthebadge.com/images/badges/cc-by.svg)](https://creativecommons.org/licenses/by/4.0/)  
This work is licensed under a [Creative Commons Attribution 4.0
International License](https://creativecommons.org/licenses/by/4.0/).
